Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-09-06 paper/ms.tex
[WIP] update ms for clarity (LAH suggestions)
Co-authored-by: Lynne Hillenbrand <lah@astro.caltech.edu>

% 250 word max!
\begin{abstract}
  %
  Complex periodic variables (CPVs) are stars that exhibit sharp and
  periodic optical light curves.  Previous work has shown that such
  stars tend to be disk-free pre-main-sequence M dwarfs with rotation
  periods of 0.2--2 days.  To advance understanding of these enigmatic
  objects, we performed a blind CPV search using TESS 2-minute data of
  \nstarssearched\ K and M dwarfs with $T$$<$16 and $d$$<$150\,pc.  We
  found \ngoods\ high-quality CPVs.  The new objects include the
  brightest ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and
  oldest ($\approx$200\,Myr) CPVs known.  All objects but one turned
  out to be likely members of stellar associations, which enabled
  age-dating.  One exceptional new object, LP 12-502, showed up to
  eight dips per cycle; the dips at times coexisted with slightly
  different periods, and the variability of the dips suggests that
  they are additive and independent.  Broadly, our search confirms
  that CPVs are mostly young ($\lesssim$150\,Myr) and low-mass
  ($\lesssim$0.4\,$M_\odot$).  The flux dips that embody the class
  have lifetimes of $\approx$100 cycles, and the dips collapse in
  response to stellar flares once every few months.  Corotating gas or
  dust clumps remain the only viable explanation.  The gas or dust is
  probably entrained by the star's magnetic field, and the sharp
  features could result from a multipolar field topology, a hypothesis
  supported by correspondences between the light curves of CPVs and of
  B stars known to have multipolar magnetic fields.
  %
\end{abstract}

@@

		\vspace{-0.65cm}
		\subfloat{
			\includegraphics[width=0.66\textwidth]{f1b.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Complex periodic variables (CPVs)}:
		{\it Top:} Phase-folded TESS light curves for three CPVs.  Each
		panel shows the average of the data accumulated over one month,
		relative to the mean stellar brightness.
		Gray circles are raw 2-minute data; black circles are binned to
		300 points per cycle.  The period in hours is printed in the
		bottom right corner.  Left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Cartoon explanations for the phenomenon.  The dust
		clump scenario (left) and gas prominence scenario (right) both invoke
		magnetically-entrained corotating material.
	}
	\label{fig:f1}
\end{figure*}

@@

In this work, we aim to find bright and nearby CPVs, since these
objects will be the most amenable to detailed photometric and
spectroscopic analyses.  To do this, we use 120-second cadence data
acquired by TESS between 2018 July and 2022 September (Sectors 1-55;
Cycles 1-4).  We present our search methods in
Section~\ref{sec:methods}, and the resulting CPV catalog in
Section~\ref{sec:results}.  The observed evolution of many CPVs over a
two-year baseline is described in Section~\ref{sec:evoln}, including a
deep-dive into the behavior of an especially interesting object, LP
12-502.  We discuss a few implications in
Section~\ref{sec:discussion}, and conclude in
Section~\ref{sec:conclusion}.

@@

We searched for CPVs by analyzing the short-cadence data acquired
by TESS between 2018 July 25 and 2022 September 1 (Sectors 1-55).
Specifically, we used the 120-second cadence light curves produced by
the Science Processing and Operations Center at the NASA Ames Research
Center \citep{2016SPIE.9913E..3EJ}.  While the TESS data products from
these sectors also included full frame images with cadences of 600 and
1800 seconds for a larger number of sources, we restricted our
attention to the 120-second data for the sake of uniformity and
simplicity in data handling.  In exchange, we sacrificed both
completeness and homogeneity of the selection function.  While TESS
cumulatively observed $\approx$90\% of the sky for at least one lunar
month between 2018 July and 2022 September, the 120-second cadence
data were collected for only a subset of observable stars that were
preferentially nearby and bright \citep[see][]{2021PASP..133i5002F}.
The total 120-second data volume
from Sectors 1-55 included 1{,}087{,}475 short-cadence light curves, which were
available for 428{,}121 unique stars.
% latter stats from MERGED_spoc2min_sector1_to_sector58.csv

To simplify our search, we defined our target sample as
stars with 120-second cadence TESS light curves satisfying the
following four conditions:
\begin{align}
  T &< 16 \quad&(\mathrm{Amenable\ with\ TESS}) \label{eq:one}\\
  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only})\\
  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})\\
  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}) \label{eq:four}.
\end{align}
Here, $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ is the Gaia
$G$-band absolute magnitude, $\varpi_{\rm as}$ is the parallax in
units of arcseconds, and $d$ is a geometric distance defined by
inverting the parallax and ignoring any zero-point correction.  We
performed this selection by cross-matching TIC8.2
\citep{2019AJ....158..138S,2021arXiv210804778P} against the Gaia DR2
point-source catalog \citep{2018A&A...616A...1G}.  We opted for Gaia
DR2 rather than DR3 because the base catalog for TIC8 was Gaia DR2,
which facilitated a one-to-one crossmatch using the Gaia source
identifiers.  The target sample ultimately included \nstarssearched\ M
dwarfs and late-K dwarfs, down to $T$$<$16 and out to $d$$<$150\,pc.
For stars with multiple sectors of TESS data available, we searched
for CPV signals independently.
In total, our \nstarssearched\ star target list included \nlcssearched\ month-long light
curves.

@@

\begin{figure}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.43\textwidth]{f2.pdf}
		\vspace{-0.2cm}
		\caption{
			{\bf Completeness of the TESS 2-minute data for late-K
      and early M dwarfs near the Sun, from Sectors 1-55.}  
      The orange dotted curve shows the number of stars in successive
      radial shells, each with a width of 10\,pc.  To be part of our selection function,
      these stars must meet the listed conditions: they must be red dwarf
      stars
      ($\bprp$>$1.5$; $M_{\rm G}$>4) amenable for TESS
      observations ($T$<16).  The blue solid curve shows the fraction
      of such stars with at least one sector of TESS 2-minute cadence
      data acquired between Sectors 1-55.
		}
			\vspace{-0.5cm}
		\label{fig:completeness}
	\end{center}
\end{figure}

@@

Prior to this study, most CPVs have been found by visually examining
all the light curves of stars in young clusters
\citep{2016AJ....152..114R,2017AJ....153..152S,2023ApJ...945..114P},
or by flagging light curves with short periods and a large number of
strong Fourier harmonics for visual inspection
\citep{2019ApJ...876..127Z}.  In this work, we implemented a new
search approach based on counting the number of sharp local minima in
phase-folded light curves, while also using the Fourier approach.  We
applied these two search techniques independently.

@@

For our dip-counting pipeline, we began with the {\tt PDC\_SAP} light
curves for each sector, removed non-zero quality flags, and normalized
the light curve by dividing out its median value.  We then flattened
the light curve using a 5-day sliding median filter, as implemented in
\texttt{wotan} \citep{2019AJ....158..143H}.  We computed a periodogram
of the resulting cleaned and flattened light curve, opting for the
\citet{1978ApJ...224..953S} phase dispersion minimization (PDM)
algorithm implemented in \texttt{astrobase}
\citep{2021zndo...1011188B} due to its shape agnosticism.  If a period
$P$ below 2 days was identified, we reran the periodogram at a finer
grid to improve the accuracy of the period determination.

@@

In short, CPV candidates were identified by requiring a peak PDM period
below two days and the presence of at least three sharp local minima,
based on at least one sector of the TESS 120-second data. Candidates
were then inspected visually as described in
Section~\ref{subsec:visual}.

@@

We performed an independent search using a Fourier-based approach,
following \citet{2019ApJ...876..127Z} and \citet[][their
Section~1.3]{2023MNRAS.524.4220P}.  Starting with the {\tt PDC\_SAP}
light curves, we normalized each light curve, and then re-binned it
into equal width 120-second bins to account for the uneven spacing in
the TESS data, as well as the data gap caused by satellite downlink
during each sector.  We then padded the data to ensure that the light
curve had a length that was a power of two, as described by
\citeauthor{2019ApJ...876..127Z}.  After taking the Fourier transform
of the padded light curve using {\tt numpy.fft}, we searched for peaks
with a significance exceeding 12-$\sigma$ within a set of 500
frequency bins.

If a peak of such significance was found, we generated a ``summary
sheet'' with information about the star, its full and folded light
curves, Fourier transform, potential contaminating stars, and
information about these contaminating stars.  Summary sheets were
generated for $\approx$10\% of the 20{,}000 120-second targets in each
sector.  We reviewed each summary sheet and tried to classify each
light curve based on visual inspection of its morphology (with
categories including eclipsing binary, CPV, RS CVn, and cataclysmic
variable). Whenever a CPV was identified, the light curves from
multiple sectors were stitched together and analyzed jointly, for a
more accurate period determination.

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f3.pdf}
		\vspace{-0.3cm}
		\caption{
      {\bf Validation plots used to classify CPVs}.  The complete figure
      set, with one image per sector for each of the \nallcands\
      objects in Table~\ref{tab:thetable} is available in the online
      journal. {\bf For internal collaboration review:
      \url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
      Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
      The adopted period is given in the lower-right corner.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
      {\it c)}: DSS finder chart, with 21$''$ and 42$''$ radius
      circles for scale.  One TESS pixel has a full side length of
      21$''$.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
      {\it k)}: Gaia DR2 color--absolute magnitude diagram. The gray
      background denotes stars within 100\,pc from
      \citet{2021A&A...649A...6G}.
      {\it l)}: Information from Gaia DR2, TIC8, and the automated
      dip-counting search pipeline.  ``Neighbors'', abbreviated
      ``nbhr'', are listed within apparent distances of 2 TESS pixels
      if $\Delta T$$<$2.5.
      {\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities,
      calculated using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

We assessed whether the objects found using the dip-counting
(Section~\ref{subsec:counting}) and Fourier
(Section~\ref{subsec:fourier}) techniques were consistent with
expectations for CPVs by assembling the data shown in
Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CPV if it met
all of the following criteria for at least one TESS sector:
\vspace{-2pt}
\begin{itemize}[leftmargin=*]
  \setlength\itemsep{-2pt}
  \item $P<2$\,days.
  %
  \item At least three dips per cycle, or else otherwise
    oddly-shaped dips.
  %
  \item Dip phases mostly repeat over $\approx$30\,day sector duration.
\end{itemize}
\vspace{-2pt}
We also noted ''possible'' CPVs for which the classification was more
ambiguous, and ``false positives'' that are definitely not CPVs.  The
most common false positives for both the Fourier and dip-counting
techniques were eclipsing binaries, ordinary spotted rapid rotators,
and complex light curves due to multiple stars contributing to the
photometric aperture.  Our dip-counting pipeline flagged
\nuniqdipflagged\ unique stars for visual inspection; about 20\% were
subsequently labeled either good or possible CPVs.  From the Fourier
pipeline, $\approx$0.5\% of stars that passed the 12-$\sigma$ peak
threshold were eventually classified as CPVs.  This is because the
Fourier pipeline was implemented as a general variability search; its
results are also being used for analyses on topics other than CPVs.

@@

\paragraph{Ages}
We estimated the stellar ages by making probabilistic spatial and
kinematic associations between the CPVs and known clusters in the solar
neighborhood.  For most stars in our sample, we did this using
BANYAN\,$\Sigma$
\citep{2018ApJ...856...23G}.\footnote{\url{https://github.com/jgagneastro/banyan_sigma},
git commit \texttt{394b486}} This algorithm calculates the probability
that a given star belongs to one of 27 young clusters (or
``associations'') within 150\,pc of the Sun, by modeling the clusters
as multivariate Gaussian distributions in 3-D position and 3-D
velocity space.  We used the Gaia DR2 sky positions, proper motions,
and distances to calculate the membership probabilities.
BANYAN\,$\Sigma$ in turn analytically marginalizes over the radial
velocity dimension.  The probabilities returned by this procedure are
qualitatively useful, but should be interpreted with caution because
the assumption of Gaussian distributions is questionable for most
groups within the solar neighborhood \citep[see
e.g.][Figure~10]{2021ApJ...917...23K}.

For a few cases where BANYAN\,$\Sigma$ yielded ambiguous results, we
consulted the meta-catalog of young, age-dated, and age-dateable stars
provided by \citet{2022AJ....163..121B}, and also searched the local
volume around each star for co-moving
companions.\footnote{\url{https://github.com/adamkraus/Comove}, git
commit \texttt{278b372}}

\paragraph{Effective temperatures, radii, and masses}

We determined the stellar effective temperature and radii by fitting
the broadband spectral energy distributions (SEDs); we then estimated
the masses by interpolating against the sizes, temperatures, and ages
of the PARSEC v1.2S models
\citep{2012MNRAS.427..127B,2014MNRAS.444.2525C}.

@@

@@

Table~\ref{tab:thetable} lists the \nallcands\ objects identified by
our search.  The \ngoods\ stars in the ``good'' sample demonstrated
what we deemed to be the key characteristics of the CPV phenomenon in
at least one TESS sector.  The classification of \nmaybes\ CPV
candidates was ambiguous, and the \ndebunked\ remaining objects were
notable false positives that we discuss below.  The \texttt{quality}
column in the table divides the three classes; additional data from
TESS or other instruments could help resolve the classification of the
ambiguous cases.   Of the \ncqvsnodebunked\ CPVs and candidate CPVs,
\nbothdipfourier\ were found using both the dip-counting and Fourier
techniques, \nyesdipnofourier\ were found using only the dip-counting
technique, and \nyesfouriernodip\ were found using only the Fourier
technique.  In the following, we will focus our discussion on the good
sample, irrespective of discovery method.  We will often refer to
stars by their TIC identifiers; the easiest way to reference these
against the figures in most document readers is to use a
``find'' ({\tt Ctrl+F}) utility.

Figure~\ref{fig:cqvs} is a mosaic of phased light curves for the
\ngoods\ CPVs.  The objects are sorted first in order of the number of
TESS 120-second cadence sectors in which they clearly demonstrated the
CPV phenomenon, and secondarily by descending brightness.  The top
five objects by this metric are TIC~300651846 ($T$$=$13.5, 12
sectors); TIC~402980664 ($T$$=$11.1, 7 sectors); TIC~89463560
($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5 sectors); and
TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CPVs span
9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
fastest five have periods spanning 3.6\,hr$<$$P$$<$6.2\,hr, and the
slowest five span 27\,hr$<$$P$$<$38\,hr.

@@

\subsection{Ages}

>>>>

% 250 word max!
\begin{abstract}
  %
  Complex periodic variables (CPVs) are stars that exhibit sharp and
  periodic optical light curves.  Previous work has indicated that such stars
  tend to be disk-free pre-main-sequence M dwarfs with rotation
  periods of 0.2--2 days.  To advance understanding of these enigmatic
  objects, we performed a blind search using TESS 2-minute data of
  \nstarssearched\ K and M dwarfs with $T$$<$16 and $d$$<$150\,pc.  We
  found \ngoods\ high-quality CPVs.  The new objects include the
  brightest ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and
  oldest ($\approx$200\,Myr) CPVs known.  All objects but one turned
  out to be likely members of stellar associations, which enabled
  age-dating.  An exceptional new object, LP 12-502, showed up to
  eight flux dips per cycle; some of the LP 12-502 dips coexisted with slightly
  different periods, and the shortest-duration LP 12-502 dips matched the expected
  timescale for transiting small bodies at the corotation radius.
  Broadly, our search confirms
  that CPVs are mostly young ($\lesssim$150\,Myr) and low-mass
  ($\lesssim$0.4\,$M_\odot$).  The flux dips that embody the class
  have lifetimes of $\approx$100 cycles, and the dips collapse in
  response to stellar flares once every few months.  Corotating
  concentrations of gas or dust remains the only plausible explanation
  known.  The gas or dust is probably entrained by the star's magnetic
  field, and the sharp features could result from a multipolar field
  topology, a hypothesis supported by correspondences between the
  light curves of CPVs and of B stars known to have multipolar
  magnetic fields.
  %
\end{abstract}

@@

		\vspace{-0.65cm}
		\subfloat{
			\includegraphics[width=0.66\textwidth]{f1b.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Complex periodic variables (CPVs)}:
		{\it Top:} Phase-folded TESS light curves for three CPVs.  Each
		panel shows the average of the data accumulated over one month,
		relative to the mean stellar brightness.
		Gray circles are raw 2-minute data; black circles are binned to
		300 points per cycle.  The period in hours is printed in the
		bottom right corner.  Left-to-right, the objects are LP 12-502
    (TIC~402980664; Sector~19), TIC~94088626 (Sector 10), and
    TIC~425933644 (Sector~28).
		{\it Bottom:} Cartoon explanations for the phenomenon.  The dust
		clump scenario (left) and gas prominence scenario (right) both invoke
		magnetically-entrained corotating material.
	}
	\label{fig:f1}
\end{figure*}

@@

In this work, we aim to find bright and nearby CPVs, since these
objects will be the most amenable to detailed photometric and
spectroscopic analyses.  To do this, we use 2-minute cadence data
acquired by TESS between 2018 July and 2022 September (Sectors 1-55;
Cycles 1-4).  We present our search methods in
Section~\ref{sec:methods}, and the resulting CPV catalog in
Section~\ref{sec:results}.  The observed evolution of many CPVs over a
two-year baseline is described in Section~\ref{sec:evoln}, including a
deep-dive into the behavior of an especially interesting object, LP
12-502.  We discuss a few implications in
Section~\ref{sec:discussion}, and conclude in
Section~\ref{sec:conclusion}.

@@

We searched for CPVs by analyzing the short-cadence data acquired
by TESS between 2018 July 25 and 2022 September 1 (Sectors 1-55).
Specifically, we used the 2-minute cadence light curves produced by
the Science Processing and Operations Center at the NASA Ames Research
Center \citep{2016SPIE.9913E..3EJ}.  While the TESS data products from
these sectors also included full frame images with cadences of 10 and
30 minutes for a larger number of sources, we restricted our
attention to the 2-minute data for the sake of uniformity and
simplicity in data handling.  In exchange, we sacrificed both
completeness and homogeneity of the selection function.  While TESS
cumulatively observed $\approx$90\% of the sky for at least one lunar
month between 2018 July and 2022 September, the 2-minute cadence
data were collected for only a subset of observable stars that were
preferentially nearby and bright \citep[see][]{2021PASP..133i5002F}.
The total 2-minute data volume
from Sectors 1-55 included 1{,}087{,}475 short-cadence light curves, which were
available for 428{,}121 unique stars.
% latter stats from MERGED_spoc2min_sector1_to_sector58.csv

To simplify our search, we defined our target sample as
stars with 2-minute cadence TESS light curves satisfying the
following four conditions:
\begin{align}
  T &< 16 \quad&(\mathrm{Amenable\ with\ TESS}) \label{eq:one}\\
  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only})\\
  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})\\
  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}) \label{eq:four}.
\end{align}
Here, $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ is the Gaia
$G$-band absolute magnitude, $\varpi_{\rm as}$ is the parallax in
units of arcseconds, and $d$ is a geometric distance defined by
inverting the parallax and ignoring any zero-point correction.  We
performed this selection by cross-matching TIC8.2
\citep{2019AJ....158..138S,2021arXiv210804778P} against the Gaia DR2
point-source catalog \citep{2018A&A...616A...1G}.  We opted for Gaia
DR2 rather than DR3 because the base catalog for TIC8 was Gaia DR2,
which facilitated a one-to-one crossmatch using the Gaia source
identifiers.  The target sample ultimately included \nstarssearched\ M
dwarfs and late-K dwarfs, down to $T$$<$16 and out to $d$$<$150\,pc.
For stars with multiple sectors of TESS data available, we searched
for CPV signals independently.
In total, our \nstarssearched\ star target list included \nlcssearched\ month-long light
curves.

@@

\begin{figure}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.43\textwidth]{f2.pdf}
		\vspace{-0.2cm}
		\caption{
			{\bf Completeness of the TESS 2-minute data for late-K
      and early M dwarfs near the Sun, from Sectors 1-55.}  
      The orange dotted curve shows the number of stars in successive
      radial shells, each with a width of 10\,pc.  To be part of our selection function,
      these stars must meet the following conditions: they must be red dwarf
      stars
      ($\bprp$>$1.5$; $M_{\rm G}$>4) amenable for TESS
      observations ($T$<16).  The blue solid curve shows the fraction
      of such stars with at least one sector of TESS 2-minute cadence
      data acquired between Sectors 1-55.
		}
			\vspace{-0.5cm}
		\label{fig:completeness}
	\end{center}
\end{figure}

@@

Prior to this study, most CPVs have been found by visually examining
all the light curves of stars in young clusters
\citep{2016AJ....152..114R,2017AJ....153..152S,2023ApJ...945..114P},
or by flagging light curves with short periods and 
strong Fourier harmonics for visual inspection
\citep{2019ApJ...876..127Z}.  In this work, we implemented a new
search approach based on counting the number of sharp local minima in
phase-folded light curves, while also using the Fourier approach.  We
applied these two search techniques independently to our
\nstarssearched\ targets.

@@

For our dip-counting pipeline, we began with the {\tt PDC\_SAP} light
curves for each sector \citep{2017ksci.rept....8S}, removed non-zero quality flags, and normalized
the light curve by dividing out its median value.  We then flattened
the light curve using a 5-day sliding median filter, as implemented in
\texttt{wotan} \citep{2019AJ....158..143H}.  We computed a periodogram
of the resulting cleaned and flattened light curve, opting for the
\citet{1978ApJ...224..953S} phase dispersion minimization (PDM)
algorithm implemented in \texttt{astrobase}
\citep{2021zndo...1011188B} due to its shape agnosticism.  If a period
$P$ below 2 days was identified, we reran the periodogram at a finer
grid to improve the accuracy of the period determination.

@@

In short, CPV candidates were identified by requiring a peak PDM period
below two days and the presence of at least three sharp local minima,
based on at least one sector of the TESS 2-minute data. Candidates
were then inspected visually as described in
Section~\ref{subsec:visual}.

@@

We performed an independent search using a Fourier-based approach,
following \citet{2019ApJ...876..127Z} and \citet[][their
Section~1.3]{2023MNRAS.524.4220P}.  Starting with the {\tt PDC\_SAP}
light curves, we normalized each light curve, and then re-binned it
into equal width 2-minute bins to account for the uneven spacing in
the TESS data, as well as the data gap caused by satellite downlink
during each sector.  We then padded the data to ensure that the light
curve had a length that was a power of two, as described by
\citeauthor{2019ApJ...876..127Z}.  After taking the Fourier transform
of the padded light curve using {\tt numpy.fft}, we searched for peaks
with a significance exceeding 12-$\sigma$ within a set of 500
frequency bins.

Peaks of significance were found for $\approx$10\% of the searched
stars.  For all such cases, we generated an interim ``summary sheet''
with information about the star, its full and folded light curves,
Fourier transform, potential contaminating stars, and information
about these contaminating stars.  We then reviewed each summary sheet,
and tentatively classified each light curve based on visual inspection
of its morphology (with common categories including eclipsing binary,
CPV, RS CVn, and cataclysmic variable).
%Whenever a CPV was identified, the light curves from
%multiple sectors were stitched together and analyzed jointly, for a
%more accurate period determination.

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f3.pdf}
		\vspace{-0.3cm}
		\caption{
      {\bf Validation plots used to classify CPVs}.  The complete figure
      set, with one image per sector for each of the \nallcands\
      objects in Table~\ref{tab:thetable} is available in the online
      journal. {\bf For internal collaboration review:
      \url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
      Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
      The adopted period is given in the lower-right corner.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
      {\it c)}: DSS finder chart, with 21$''$ and 42$''$ radius
      circles for scale.  One TESS pixel has a full side length of
      21$''$.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
      {\it k)}: Gaia DR2 color--absolute magnitude diagram. The gray
      background denotes stars within 100\,pc from
      \citet{2021A&A...649A...6G}.
      {\it l)}: Information from Gaia DR2, TIC8, and the automated
      dip-counting search pipeline.  ``Neighbors'', abbreviated
      ``nbhr'', are listed within apparent distances of 2 TESS pixels
      if $\Delta T$$<$2.5.
      {\it m)}: BANYAN\,$\Sigma$ v1.2 association probabilities,
      calculated using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

We homogeneously assessed whether the objects identified using the
dip-counting (Section~\ref{subsec:counting}) and Fourier
(Section~\ref{subsec:fourier}) approaches were consistent with
expectations for CPVs by assembling the data shown in
Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CPV if it met
all of the following criteria for at least one TESS sector:
\vspace{-2pt}
\begin{itemize}[leftmargin=*]
  \setlength\itemsep{-2pt}
  \item $P<2$\,days.
  %
  \item At least three dips per cycle, or else otherwise
    oddly-shaped dips.
  %
  \item Dip phases mostly repeat over $\approx$30\,day sector duration.
\end{itemize}
\vspace{-2pt}
We also noted ''possible'' CPVs for which the classification was more
ambiguous, and ``false positives'' that are definitely not CPVs.  The
most common false positives for both the Fourier and dip-counting
techniques were eclipsing binaries, ordinary spotted rapid rotators,
and light curves that were complex due to multiple stars contributing to the
photometric aperture.  Our specialized dip-counting pipeline flagged
\nuniqdipflagged\ unique stars for visual inspection; about 20\% were
subsequently labeled either good or possible CPVs.  From the more
general Fourier pipeline, $\approx$0.5\% of stars that passed the
12-$\sigma$ peak threshold were eventually classified as CPVs.

@@

\subsubsection{Ages}
While most of our target stars were field stars, color--absolute
magnitude diagrams suggested that most CPVs tended to be on the
pre-main-sequence (e.g.\ panel {\it (k) of Figure~\ref{fig:vet}}).  We
therefore estimated stellar ages by checking for probabilistic spatial
and kinematic associations between the CPVs and known clusters in the
solar neighborhood.  For most stars in our sample, we did this using
BANYAN\,$\Sigma$
\citep{2018ApJ...856...23G}.\footnote{\url{https://github.com/jgagneastro/banyan_sigma},
git commit \texttt{394b486}} This algorithm calculates the probability
that a given star belongs to either the field, or to any of 27 young
clusters (``associations'') within 150\,pc of the Sun.  This is
achieved by modeling the field and cluster populations as multivariate
Gaussian distributions in 3-D position and 3-D velocity space.  We
used the Gaia DR2 sky positions, proper motions, and distances to
calculate the membership probabilities.  BANYAN\,$\Sigma$ in turn
analytically marginalizes over the radial velocity dimension.  The
probabilities returned by this procedure are qualitatively helpful, but
should be interpreted with caution because the assumption of Gaussian
distributions is questionable for most groups within the solar
neighborhood \citep[see e.g.][Figure~10]{2021ApJ...917...23K}.

For a few cases where BANYAN\,$\Sigma$ yielded ambiguous results, we
consulted the meta-catalog of young, age-dated, and age-dateable stars
provided by \citet{2022AJ....163..121B}, and also searched the local
volume around each star for co-moving
companions.\footnote{\url{https://github.com/adamkraus/Comove}, git
commit \texttt{278b372}}
Finally, to provide a base for comparison, we also ran the
BANYAN\,$\Sigma$ membership analysis on our entire \nstarssearched\
target star sample.

\subsubsection{Effective temperatures, radii, and masses}

We determined the stellar effective temperature and radii for the CPVs
by fitting the broadband spectral energy distributions (SEDs); we then
estimated the masses by interpolating against the sizes, temperatures,
and ages of the PARSEC v1.2S models
\citep{2012MNRAS.427..127B,2014MNRAS.444.2525C}.

@@

\subsubsection{Binarity}

The main types of binaries of interest in this work are those that
are unresolved, because they can lead to misinterpretations of the data.
For instance, unresolved binaries might produce multiple photometric
signals and hinder our ability to correctly identify the star hosting
the CPV signal.  Unresolved binaries could also bias photometric magnitude
and color measurements, which would affect our stellar parameter
estimates.  To attempt to identify binaries, we considered the
following lines of information.

{\it RUWE}---We examined plots of Gaia DR3 RUWE as a function of
color.\footnote{For an explanation of the renormalized unit weight
error (RUWE), see the GAIA DPAC technical note
\url{http://www.rssd.esa.int/doc_fetch.php?  id=3757412}.}  Elevated
RUWEs imply excess astrometric noise relative to a single-source
model.  This can be caused by marginally resolved binaries,  intrinsic
photometric variability, or intrinsic astrometric motion.  Based on
this exercise, we adopted a threshold of RUWE$_{\rm DR3}>2$ to
flag sources with excess astrometric noise.  This threshold was met
by \ngoodhighruwe/\ngoods\ high-quality CPVs and by
\nmaybehighruwe/\nmaybes\ of the ambiguous CPVs.  The choice of the threshold RUWE
is somewhat subjective, since the RUWE distribution has an extended tail
\citep[e.g.][]{2022MNRAS.513.5270P}.  If we had instead required
RUWE$_{\rm DR3}>1.4$, \ngoodweakruwe/\ngoods\ high-quality CPVs
and \nmaybeweakruwe/\nmaybes\ of the ambiguous sample would have been
flagged.

{\it Multiple periodic TESS signals}---During our visual analysis of
the TESS light curves and PDM periodograms, we flagged sources with
beating light curves, and with PDM periodograms that showed multiple
periods.  We also attempted to disentangle the two signals by
subtracting the mean CPV signal over each sector, and then repeating
the phase-dispersion minimization analysis.  The results of this effort
are summarized in the secondary periods, $P_{\rm sec}$, listed in
Table~\ref{tab:thetable}, which we required to be at least 5\%
different from the primary period.  This process yielded
\ngoodmultperiodflag/\ngoods\ high-quality CPVs with secondary
periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous sample met
the same criterion.  Of the \ngoodhighruwe\ good CPVs with ${\rm
RUWE}_{\rm DR3}> 2$, \ngoodruweandmultperiod\ also showed secondary
periods in the TESS light curves.  Considering the weaker threshold of
${\rm RUWE}_{\rm DR3}> 1.4$,
\ngoodweakruweandmultperiod/\ngoodweakruwe\ such CPVs showed secondary
TESS periods.

Table~\ref{tab:thetable} summarizes each of the sources of
binarity information into a single bitwise column.  
We present the detailed results concerning binarity in
Section~\ref{subsec:resultsbinarity}, and a summary discussion in
Section~\ref{subsec:discbinary}.

@@

Table~\ref{tab:thetable} lists the \nallcands\ objects identified by
our search.  The \ngoods\ stars in the ``good'' sample demonstrated
what we deemed to be the key characteristics of the CPV phenomenon in
at least one TESS sector.  The classification of \nmaybes\ CPV
candidates was ambiguous, and the \ndebunked\ remaining objects were
notable false positives that we discuss below.  The \texttt{quality}
column in the table divides the three classes; additional data from
TESS or other instruments could help resolve the classification of the
ambiguous cases.   Of the \ncqvsnodebunked\ CPVs and candidate CPVs,
\nbothdipfourier\ were found using both the dip-counting and Fourier
techniques, \nyesdipnofourier\ were found using only the dip-counting
technique, and \nyesfouriernodip\ were found using only the Fourier
technique.  In the following, we will focus our discussion on the good
sample, irrespective of discovery method.  We will often refer to
stars by their TIC identifiers; these can be referenced against the
figures in most digital document readers using a ``find'' ({\tt
Ctrl+F}) utility.

Figure~\ref{fig:cqvs} is a mosaic of phased light curves for the
\ngoods\ CPVs.  The objects are sorted first in order of the number of
TESS 2-minute cadence sectors in which they clearly demonstrated the
CPV phenomenon, and secondarily by descending brightness.  The top
five objects by this metric are TIC~300651846 (12 sectors);
TIC~402980664 (7 sectors); TIC~89463560
(5 sectors); TIC~363963079 (5 sectors); and
TIC~294328887 (4 sectors).  The brightest five CPVs span
9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
fastest five have periods spanning 3.6\,hr$<$$P$$<$6.2\,hr, and the
slowest five span 27\,hr$<$$P$$<$38\,hr.

@@

\subsection{Ages of CPVs}
\label{subsec:ageresults}
